Implementation and Evaluation of the Simple Network Management Protocol over IEEE 802.15.4 Radios under the Contiki Operating System\\ MSc. Thesis Proposal

### 2010-02-04 doc/msc-proposal/msc-proposal.tex
proposal: final corrections

%% Abstract page
\newpage
\begin{abstract}
IEEE 802.15.4 is a standard which specifies the physical layer and media access control for low-rate wireless personal area networks providing node-to-node frame delivery between devices within reachable distance. The standard is targeted at low-cost, low-speed and low-power devices. Simple Network Management Protocol (SNMP) is a widely deployed application protocol for network management and data retrieval. It can be very lightweight and may fit resource-constrained devices very well. The focus of the proposed work will be implementation and evaluation of the SNMP protocol for devices supporting IEEE 802.15.4 Radios and the Contiki Embedded Operating System. This document provides background information on several related areas, such as 802.15.4 standard,                          the 6LoWPAN approach for transmitting IPv6 traffic over 802.15.4 and the SNMP protocol.

@@

As preparation for this work, several related areas have been studied in more depth to collect background information. The rest of the document is organised in six chapters. Chapter \ref{ch:ieee802.15.4} provides an introduction to the IEEE 802.15.4 standard. Chapter \ref{ch:6lowpan} describes the adaptation layer that allows the transmission of IPv6 packets over 802.15.4 links. In Chapter \ref{ch:routing} 6LoWPAN routing problems are discussed. The 6LoWPAN Neighbor Discovery Protocol is covered in Chapter \ref{ch:nd}. Chapter \ref{ch:snmp} gives an overview of the Simple Network Management Protocol. Chapter \ref{ch:proposal} describes details of the proposed work to be done in the scope of the Master Thesis.

@@

Packets with a multicast IPv6 destination address are sent to the 16-bit 802.15.4 address obtained by concatenating the 3-bit multicast prefix 101, the last 5 bits in the 15-th octet and the whole 16-th octet of the multicast IPv6 address.

@@

The work will be accomplished over several phases. In the first phase, the basic SNMPv1 protocol will be implemented. Then, the focus will be shifted to creation of a secure network layer for Contiki. Finally, a security layer will be added to the SNMPv1 implementation.

>>>>

%% Abstract page
\newpage
\begin{abstract}
IEEE 802.15.4 is a standard which specifies the physical layer and media access control for low-rate wireless personal area networks providing node-to-node frame delivery between devices within reachable distance. The standard is targeted at low-cost, low-speed and low-power devices. Simple Network Management Protocol (SNMP) is a widely deployed application protocol for network management and data retrieval. Its implementation can be very lightweight and may fit resource-constrained devices very well. The focus of the proposed work will be implementation and evaluation of the SNMP protocol for devices supporting IEEE 802.15.4 Radios and the Contiki Embedded Operating System. This document provides background information on several related areas, such as 802.15.4 standard, the 6LoWPAN approach for transmitting IPv6 traffic over 802.15.4 and the SNMP protocol.

@@

As preparation for this work, several related areas have been studied in more depth to collect background information. The rest of the document is organised in six chapters. Chapter \ref{ch:ieee802.15.4} provides an introduction to the IEEE 802.15.4 standard. Chapter \ref{ch:6lowpan} describes the adaptation layer that allows the transmission of IPv6 packets over 802.15.4 links. In Chapter \ref{ch:routing} 6LoWPAN routing problems are discussed. The 6LoWPAN Neighbour Discovery Protocol is covered in Chapter \ref{ch:nd}. Chapter \ref{ch:snmp} gives an overview of the Simple Network Management Protocol. Chapter \ref{ch:proposal} describes the details of the proposed work to be done in the scope of the Master Thesis.

@@

Packets with a multicast IPv6 destination address are sent to the 16-bit 802.15.4 address obtained by concatenating the 3-bit multicast prefix 101, the last 5 bits in the 15th octet and the whole 16th octet of the multicast IPv6 address.

@@

The work will be accomplished over several phases. In the first phase, the basic SNMPv1 protocol will be implemented. Then, the focus will be shifted to the creation of a secure network layer for Contiki. Finally, a security layer will be added to the SNMPv1 implementation.
